Social_Isolation_and_Loneliness

### 2023-02-23 FEM_R/Loneliness_Social_Isolation/PAPER_WORKING_SCRIPT.Rmd
Changed path for new PC

```{r setup, include=FALSE}
# Need to set up the working directory
workingDir <- "/home/luke/Documents/E_FEM_clean/E_FEM/"
knitr::opts_knit$set(root.dir = workingDir)

>>>>

```{r setup, include=FALSE}
# Need to set up the working directory
workingDir <- "/home/luke/Documents/WORK/E_FEM/E_FEM/"
knitr::opts_knit$set(root.dir = workingDir)
